---
title: "About"
---

# Methodology

All the data preparation has been made with R scripts to aggregate and prepare the data for this viewer tool. These scripts are available [here](https://github.com/rysebaert/nepal_expe/tree/main/R). It basically follows a 2-steps procedure :

- Find geolocation for peaks
- Create indicators aggregated at peaks and country level that are displayed in the dashboard.

## Peak geocoding

The Himalayan database is organized in several .dbf files which give information on peaks, expeditions and expeditions members.  

Howewer, no information related to peak geolocation is given by the database. It has been done for all the peaks above 6700 meters (159 over the 479 Nepal Peaks). 

Geolocation have been obtained following 3 steps based on the name of the peak included in the Himalayan database :

- Get the geolocation based on a query on the Wikipedia database with the `wikidataR` package.
- If the peaks locations haven't been found, try to extract this information from the OpenStreetMap database and the `osmextract` R package.
- For the rest, manual completion with personal survey and checks, mainly processed thanks to the list provided by the Nepal [Himal Peak Profile](https://nepalhimalpeakprofile.org/peak-profile/all-peaks) website. In this step, some unknown location peaks have been aggregated. For instance, Fang and Glacier Dome have been rattached to Annapurna I peak, Churen Himal Central, East and West (no precise location found) have been aggregated to Churen, Domo Kang and Domo to Domo, etc. 

All this consolidation output can be found in [this file](https://github.com/rysebaert/nepal_expe/blob/main/data_conso/peaks_osm_wiki_6700.csv). If the column wiki is set by 1, it means that the location of the peak has been identified with Wikipedia. If osm, osm.x and osm.y is defined by 1 value, it means that peak coordinates has been identified with OpenStreetMap (OSM value *name*, *int_name* and *en_name*). Finally the column PKCONSO gives aggregated name for undefined locations (14 peaks).

This consolidation process could for sure be improved. But, well, it works at the moment :-)



## Indicator creation

Two datasets have been created, 1 for each of the 159 peaks and one at country level based on expedition members statistics. Data has been created based on peak identifier and country of belonging of expedition members.

For this dataset, at [table of correspondence](https://github.com/rysebaert/nepal_expe/blob/main/data_conso/ISO3_CITIZENSHIP.csv) has been created to make possible the relationship between entries included in the `members.dbf` file and official international ISO-3 codes. Some choices have been made in that order :

- **Former countries** : Citizenship related to Czechoslovakia has been rattached to Czech Republic and Yugoslavia to Serbia. 
- **Several citizenship declared** : When several citizenship appear (e.g. *Ukraine/Azerbaijan*), the first one is only kept (*Ukraine* in this case).


# Consolidated datasets

2 geojson files are created, 1 is used for peak visualization and 1 for expedition members at country level. The column is the description shows if the data is used for the mapping or not (stock for proportional circles, ratio for color palettes other being not directly mapped but can be used for labeling).

## Peak indicators

```{r}
#| echo: false
#| label: tbl-1
#| tbl-cap: "Listing of consolidated indicators for peaks above 6700m"
library(kableExtra) # Table formatting
meta <- read.csv("data_conso/metadata.csv")

kable(meta, booktabs = T)
```


## Country indicators

```{r}
#| echo: false
#| label: tbl-2
#| tbl-cap: "Listing of consolidated indicators at country level"
library(kableExtra) # Table formatting
meta <- read.csv("data_conso/metadata_world.csv")

kable(meta, booktabs = T)
```


# Citation

For attribution, please cite this work as:

BibTeX citation : 

```{markdown}
@online{ysebaert,
  author = {Ronan Ysebaert},
  editor = {},
  title = {Nepal expeditions wiewer},
  date = {2024},
  langid = {en}
}
```

[Ysebaert Ronan](https://rysebaert.gitpages.huma-num.fr/cv/), 2024, Nepal expeditions viewer.


<p align="center">
[![License: CC BY-SA 4.0](https://img.shields.io/badge/License-CC%20BY--SA%204.0-lightgrey.svg)](http://creativecommons.org/licenses/by-sa/4.0/)
</p>


